\clearpage

\subsection{\bf rollrec}

{\bf NAME}

\path{rollrec} - Rollover-related zone data used by DNSSEC-Tools programs.

{\bf DESCRIPTION}

{\it rollrec} files contain data used by the DNSSEC-Tools to manage key
rollover.  A {\it rollrec} file is organized in sets of {\it rollrec} records.
Each {\it rollrec} describes the rollover state of a single zone and must be
either of {\it roll} type or {\it skip} type.  Zone {\it rollrec}s record
information about currently rolling zones.  Skip {\it rollrec}s record
information about zones that are not being rolled.  A {\it rollrec} consists
of a set of keyword/value entries.

The DNSSEC-Tools {\bf rollrec.pm} module manipulates the contents of a {\it
rollrec} file.  Module interfaces exist for looking up {\it rollrec} records,
creating new records, and modifying existing records.

Comment lines and blank lines are ignored by the DNSSEC-Tools programs.
Comment lines start with either a `\#' character or a `$;$' character.

{\bf FIELDS}

The fields in a {\it rollrec} record are:

\begin{itemize}

\item {\it curphase}

The zone's current rollover phase.  A value of zero indicates that the zone
is not in rollover, but is in normal operation.  A value of 1, 2, 3, 4
indicates that the zone is in that rollover phase.

\item {\it display}

This boolean field indicates whether or not the zone should be displayed by
the \cmd{blinkenlights} program.

\item {\it keyrec}

The zone's {\it keyrec} file.

\item {\it maxttl}

The maximum time-to-live for the zone.  This is measured in seconds.

\item {\it phasestart}

The time-stamp of the beginning of the zone's current phase.

\item {\it zonefile}

The zone's zone file.

\end{itemize}

\clearpage
{\bf EXAMPLES}

The following is an example of a roll {\it rollrec}:

\begin{verbatim}
    roll "example.com"
            zonefile      "example.com.signed"
            keyrec        "example.com.krf"
            curphase      "1"
            maxttl        "60"
            display       "1"
            phasestart    "Mon Nov 13 19:31:26 2006"
\end{verbatim}

The following is an example of a skip {\it rollrec}:

\begin{verbatim}
    skip "test.com"
            zonefile      "test.com.signed"
            keyrec        "test.com.krf"
            curphase      "0"
            maxttl        "60"
            display       "1"
            phasestart    "Mon Nov 13 19:31:50 2006"
\end{verbatim}

{\bf SEE ALSO}

\cmd{lsroll(1)}

\cmd{blinkenlights(8)},
\cmd{rollerd(8)},
\cmd{zonesigner(8)}

\perlmod{Net::DNS::SEC::Tools::keyrec.pm(3)},
\perlmod{Net::DNS::SEC::Tools::rollrec.pm(3)}

\path{keyrec(5)}
