\clearpage

\subsection{\bf blinkenlights.conf}

{\bf NAME}

\path{blinkenlights.conf} - Configuration file for the DNSSEC-Tools
\cmd{blinkenlights} program.

{\bf DESCRIPTION}

This file contains configuration information for the DNSSEC-Tools
\cmd{blinkenlights} program.  These configuration data are used as default
values The {\bf conf.pm} module is used to parse this configuration file.

A line in this file contains either a comment or a configuration
entry.  Comment lines start with either a `\#' character or a `$;$' character.
Comment lines and blank lines are ignored by the DNSSEC-Tools programs.

Configuration entries are in a {\it keyword/value} format.  The keyword is a
character string that contains no whitespace.  The value is a tokenized list
of the remaining character groups, with each token separated by a single space.

True/false flags must be given a true or false value.
True values are:  1, ``yes'', ``on''.
False values are:  0, ``no'', ``off''.

{\bf Configuration Records}

The following records are recognized by \cmd{blinkenlights}.

\begin{description}

\item [colors]\verb" "

Toggle indicating whether or not to use different background colors for
\cmd{blinkenlights} zone stripes.
If on, different colors will be used.
If off, the {\it skipcolor} value will be used.

\item [fontsize]\verb" "

The font size used to display information in the {\bf blinkenlights} window.
If this is not specified, the default font size is 18.

\item [modify]\verb" "

Toggle indicating whether or not to allow access to \cmd{blinkenlights}'
zone-modification commands.  These commands are the GUI's front-end to
some of \cmd{rollerd}'s commands.
If on, the commands are enabled.
If off, the commands are disabled.

\item [shading]\verb" "

Toggle indicating whether or not to use color shading in \cmd{blinkenlights}'
status column.
If on, shading is enabled.
If off, shading is disabled.

\item [showskip]\verb" "

Toggle indicating whether or not to display skipped zones in
\cmd{blinkenlights}' window.
If on, skipped zones are displayed.
If off, skipped zones are not displayed.

\item [skipcolor]\verb" "

The background color to use in displaying skipped zones.
If this is not specified, the default color is grey.

\end{description}

{\bf Example File}

The following is an example \cmd{blinkenlights.conf} configuration file.

\begin{verbatim}
    #
    # DNSSEC-Tools configuration file for blinkenlights
    #
    #        Recognized values:
    #                colors        use different colors for stripes (toggle)
    #                fontsize      size of demo output font
    #                modify        allow modification commands (toggle)
    #                shading       shade the status columns (toggle)
    #                showskip      show skipped zones (toggle)
    #                skipcolor     color to use for skip records

    fontsize        24
    modify          no

    colors          on
    skipcolor       orange
    showskip        1
    shading         yes
\end{verbatim}

{\bf SEE ALSO}

\cmd{blinkenlights(8)},
\cmd{rollerd(8)}

\perlmod{Net::DNS::SEC::Tools::conf.pm(3)}
