\clearpage

\subsection{\bf libval Library}

{\bf NAME}

\func{val\_resolve\_and\_check()}, \func{val\_free\_result\_chain()} - query
and validate answers from a DNS name server

\func{val\_istrusted()} - check if status value corresponds to that of a
trustworthy answer

\func{val\_isvalidated()} - check if status value represents an
answer that was cryptographically validated up to a configured
trust anchor

\func{val\_create\_context()}, \func{val\_free\_context()},
\func{val\_switch\_policy\_scope()} - manage validator context

\func{dnsval\_conf\_get()}, \func{resolver\_config\_get()},
\func{root\_hints\_get()} - get the current location for the validator
configuration files

\func{dnsval\_conf\_set()}, \func{resolver\_config\_set()},
\func{root\_hints\_set()} - set the current location for the validator
configuration files

\func{p\_ac\_status()}, \func{p\_val\_status()} - display validator status
information

{\bf SYNOPSIS}

\begin{verbatim}
    #include <validator.h>

    int val_resolve_and_check(val_context_t            *context,
                              u_char                   *domain_name_n,
                              const u_int16_t          type,
                              const u_int16_t          class,
                              const u_int8_t           flags,
                              struct val_result_chain  **results);

    void val_free_result_chain(struct val_result *results);

    int val_istrusted(val_status_t val_status);

    int val_create_context(const char *label, val_context_t **newcontext);

    void val_free_context(val_context_t *context);

    char *resolver_config_get(void);

    int resolver_config_set(const char *name);

    char *root_hints_get(void);

    int root_hints_set(const char *name);

    char *dnsval_conf_get(void);

    int dnsval_conf_set(const char *name);

    char *p_ac_status(val_astatus_t valerrno);

    char *p_val_status(val_status_t valerrno);
\end{verbatim}

{\bf DESCRIPTION}

The \func{val\_resolve\_and\_check()} function queries a set of name servers
for the \var{$<$domain\_name\_n, type, class$>$} tuple and to verifies and
validates the response.  Verification involves checking the RRSIGs, and
validation is verification up the chain-of-trust to a trust anchor.  The
\var{domain\_name\_n} parameter is the queried name in DNS wire format.  The
conversion from host format to DNS wire format can be done using the
\func{ns\_name\_pton()} function exported by the \lib{libsres(3)} library.

Answers returned by \func{val\_resolve\_and\_check()} are made available in
the \var{*results} array.  Each answer is a distinct RRset; multiple RRs
within the RRset are treated as the same answer.  Multiple answers are
possible when \var{type} is \var{ns\_t\_any}.

Individual elements in \var{*results} point to the authentication chain
contained within the \\
\func{val\_authentication\_chain} linked list.  The
authentication chain elements contain the actual RRsets returned by the name
server in response to the query.

Most applications only require the status value within \var{*results} since
this provides a single error code for representing the authenticity of
returned data.  Other more intrusive applications, such as a DNSSEC
troubleshooting utility, may look at individual authentication chain elements
to identify what particular component in the chain-of-trust led to a
validation failure.  \func{val\_istrusted()} is a helper function that easily
identifies if a given validator status value corresponds to one of the
authenticated and/or trusted data codes.  Validator status values returned in
the \var{val\_result\_chain} and \var{val\_authentication\_chain} linked lists
can be can be converted into ASCII format using the \func{p\_val\_status()}
and \func{p\_ac\_status()} functions.

The \lib{libval} library internally allocates memory for \var{*results} and
this must be freed by the invoking application using the
\func{free\_result\_chain()} interface.

The first parameter to \func{val\_resolve\_n\_check()} is the validator
context.  Applications can create a new validator context using the
\func{val\_create\_context()} function.  This function parses the resolver and
validator configuration files and creates the handle \var{newcontext} to this
parsed information.  Information stored as part of validator context includes
the validation policy and resolver policy.  Validator and resolver policy are
read by default from the \path{/etc/dnsval.conf} and \path{/etc/resolv.conf}
files.  ``Root hints'' that allows the library to bootstrap its lookup process
when functioning as a full resolver is read from \path{/etc/root.hints}.  The
locations of each of these files may be changed using the
interfaces \func{dnsval\_conf\_set()}, \func{resolver\_config\_set()}, and
\func{root\_hints\_set()}, respectively.  The corresponding ``get'' interfaces
(namely {\it dnsval\_conf\_get()}, {\it resolver\_config\_get()}, and {\it
root\_hints\_get()}) can be used to return the current location from where
these configuration files are read.

Applications can use local policy to influence the validation outcome.
Examples of local policy elements include trust anchors for different zones
and untrusted algorithms for cryptographic keys and hashes.  Local policy may
vary for different applications and operating scenarios.

Local policy for the validator is stored in the configuration file,
\path{/etc/dnsval.conf}.  Policies are identified by simple text strings
called labels, which must be unique within the configuration system.  For
example, ``browser'' could be used as the label that defines the validator
policy for all web-browsers in a system.  A label value of ``:'' identifies
the default policy, the policy that is used when a NULL context is specified
as the \var{ctx} parameter for interfaces such as
\func{val\_resolve\_and\_check()}, \func{val\_getaddrinfo()}, and
\func{val\_gethostbyname()}.  The default policy is unique within the
configuration system.

{\bf DATA STRUCTURES}

\begin{description}

\item \struct{struct val\_result\_chain}\verb" "

\begin{verbatim}
    struct val_result_chain
    {
        val_status_t                     val_rc_status;
        struct val_authentication_chain *val_rc_answer;
        int                              val_rc_proof_count;
        struct val_authentication_chain *val_rc_proofs[MAX_PROOFS];
        struct val_result_chain         *val_rc_next;
    };
\end{verbatim}

\begin{description}

\item \var{val\_rc\_answer}\verb" "

Authentication chain for a given RRset.

\item \var{val\_rc\_next}\verb" "

Pointer to the next RRset in the set of answers returned for a query.

\item \var{val\_rc\_proofs}\verb" "

Pointer to any proofs that were returned for the query.

\item \var{val\_rc\_proof\_count}\verb" "

Number of proof elements stored in \var{val\_rc\_proofs}.

\item \var{val\_rc\_status}\verb" "

Validation status for a given RRset.  This can be one of the following:

\begin{itemize}

\item \const{VAL\_SUCCESS}\verb" "

Answer received and validated successfully.

\item \const{VAL\_LOCAL\_ANSWER}\verb" "

Answer was available from a local file.

\item \const{VAL\_BARE\_RRSIG}\verb" "

No DNSSEC validation possible, query was for an RRSIG.

\item \const{VAL\_NONEXISTENT\_NAME}\verb" "

No name was present and a valid proof of non-existence confirming the missing
name (NSEC or NSEC3 span) was returned. The components of the proof were also
individually validated.

\item \const{VAL\_NONEXISTENT\_TYPE}\verb" "

No type exists for the name and a valid proof of non-existence confirming the
missing name (NSEC or NSEC3 span) was returned.  The components of the proof
were also individually validated.

\item \const{VAL\_NONEXISTENT\_NAME\_NOCHAIN}\verb" "

No name was present and a valid proof of non-existence confirming the missing
name (NSEC or NSEC3 span) was returned. The components of the proof were also
identified to be trustworthy, but they were not individually validated.

\item \const{VAL\_NONEXISTENT\_TYPE\_NOCHAIN}\verb" "

No type exists for the name and a valid proof of non-existence confirming the
missing name (NSEC or NSEC3 span) was returned.  The components of the proof
were also identified to be trustworthy, but they were not individually
validated.

\item \const{VAL\_ERROR}\verb" "

Did not have sufficient or relevant data to complete validation, or
encountered a DNS error.

\item \const{VAL\_DNS\_ERROR\_BASE} $+$ \const{SR\_}{\it error}\verb" "

This value contains a resolver error from \lib{libsres}.  The \lib{libsres}
error is \\
added to \const{VAL\_DNS\_ERROR\_BASE}, so this value will lie between \\
\const{VAL\_DNS\_ERROR\_BASE} and \const{VAL\_DNS\_ERROR\_LAST}.

\item \const{VAL\_INDETERMINATE}\verb" "

Lacking information to give a more conclusive answer.

\item \const{VAL\_BOGUS}\verb" "

Validation failure condition.

\item \const{VAL\_NOTRUST}\verb" "

All available components in the authentication chain verified properly, but
there was no trust anchor available.

\item \const{VAL\_IGNORE\_VALIDATION}\verb" "

Local policy was configured to ignore validation for the zone from which this
data was received.

\item \const{VAL\_TRUSTED\_ZONE}\verb" "

Local policy was configured to trust any data received from the given zone.

\item \const{VAL\_UNTRUSTED\_ZONE}\verb" "

Local policy was configured to reject any data received from the given zone.

\item \const{VAL\_PROVABLY\_UNSECURE}\verb" "

The record or some ancestor of the record in the authentication chain towards
the trust anchor was known to be provably unsecure.

\end{itemize}

Error values in \var{val\_status\_t} returned by the validator can be displayed
in a more user-friendly format using \func{p\_val\_status()}.

\end{description}

\item \struct{struct val\_authentication\_chain}\verb" "

\begin{verbatim}
    struct val_authentication_chain
    {
        val_astatus_t                    val_ac_status;
        struct val_rrset                *val_ac_rrset;
        struct val_authentication_chain *val_ac_trust;
    };
\end{verbatim}

\begin{description}

\item \var{val\_ac\_status}\verb" "

Validation state of the authentication chain element.  This field will contain
the error or success code for DNSSEC validation over the current authentication
chain element upon completion of \func{val\_resolve\_n\_check()}.  This field
may contain the following values:

\begin{description}

\item \const{VAL\_AC\_UNSET}\verb" "

The status was not set.

\item \const{VAL\_AC\_DATA\_MISSING}\verb" "

No data were returned for a query and the DNS did not indicate an error.

\item \const{VAL\_AC\_RRSIG\_MISSING}\verb" "

RRSIG data could not be retrieved for a resource record.

\item \const{VAL\_AC\_DNSKEY\_MISSING}\verb" "

The DNSKEY for an RRSIG covering a resource record could not be retrieved.

\item \const{VAL\_AC\_DS\_MISSING}\verb" "

The DS record covering a DNSKEY record was not available.

\item \const{VAL\_AC\_UNTRUSTED\_ZONE}\verb" "

Local policy defined a given zone as untrusted, with no further validation
being deemed necessary.

\item \const{VAL\_AC\_UNKNOWN\_DNSKEY\_PROTOCOL}\verb" "

The DNSKEY protocol number was unrecognized.

\item \const{VAL\_AC\_NOT\_VERIFIED}\verb" "

All RRSIGs covering the RRset could not be verified.

\item \const{VAL\_AC\_VERIFIED}\verb" "

At least one RRSIG covering a resource record had a status of \\
\const{VAL\_AC\_RRSIG\_VERIFIED}.

\item \const{VAL\_AC\_LOCAL\_ANSWER}\verb" "

The answer was obtained locally (e.g., from \path{/etc/hosts}) and validation
was not performed on the results.

\item \const{VAL\_AC\_TRUST\_KEY}\verb" "

A given DNSKEY or a DS record was locally defined to be a trust anchor.

\item \const{VAL\_AC\_IGNORE\_VALIDATION}\verb" "

Validation for the given resource record was ignored, either because of some
local policy directive or because of some protocol-specific behavior.

\item \const{VAL\_AC\_TRUSTED\_ZONE}\verb" "

Local policy defined a given zone as trusted, with no further validation being
deemed necessary.

\item \const{VAL\_AC\_PROVABLY\_UNSECURE}\verb" "

The authentication chain from a trust anchor to a given zone could not be
constructed due to the provable absence of a DS record for this zone in the
parent.

\item \const{VAL\_AC\_BARE\_RRSIG}\verb" "

The response was for a query of type RRSIG.  RRSIGs contain the cryptographic
signatures for other DNS data and cannot themselves be validated.

\item \const{VAL\_AC\_NO\_TRUST\_ANCHOR}\verb" "

There was no trust anchor configured for a given authentication chain.

\item \const{VAL\_DNS\_ERROR\_BASE} $+$ \const{SR\_}{\it error}\verb" "

This value contains a resolver error from \lib{libsres}.  The \lib{libsres}
error is added \\
to \const{VAL\_DNS\_ERROR\_BASE}, so this value will lie between \\
\const{VAL\_DNS\_ERROR\_BASE} and \const{VAL\_DNS\_ERROR\_LAST}.
These values include the following:

\begin{itemize}

\item \const{SR\_CONFLICTING\_ANSWERS} - Multiple conflicting answers received
for a query.

\item \const{SR\_REFERRAL\_ERROR} - Some error encountered while following
referrals.

\item \const{SR\_MISSING\_GLUE} - Glue was missing.

\end{itemize}

\end{description}

\item \var{val\_ac\_rrset}\verb" "

Pointer to an RRset of type \struct{struct val\_rrset} obtained from the DNS
response.

\item \var{val\_ac\_trust}\verb" "

Pointer to an authentication chain element that either contains a DNSKEY RRset
that can be used to verify RRSIGs over the current record, or contains a DS
RRset that can be used to build the chain-of-trust towards a trust anchor.

\end{description}

\item \struct{struct val\_rrset}\verb" "

\begin{verbatim}
    struct val_rrset
    {
        u_int8_t      *val_msg_header; 
        u_int16_t      val_msg_headerlen;
        u_int8_t      *val_rrset_name_n; 
        u_int16_t      val_rrset_class_h;
        u_int16_t      val_rrset_type_h;
        u_int32_t      val_rrset_ttl_h;
        u_int8_t       val_rrset_section;
        struct rr_rec *val_rrset_data;
        struct rr_rec *val_rrset_sig;
    };
\end{verbatim}

\begin{description}

\item \var{val\_msg\_header}\verb" "

Header of the DNS response in which the RRset was received.

\item \var{val\_msg\_headerlen}\verb" "

Length of the header information in \var{val\_msg\_header}.

\item \var{val\_rrset\_name\_n}\verb" "

Owner name of the RRset represented in on-the-wire format.

\item \var{val\_rrset\_class\_h}\verb" "

Class of the RRset.

\item \var{val\_val\_rrset\_type\_h}\verb" "

Type of the RRset.

\item \var{val\_rrset\_ttl\_h}\verb" "

TTL of the RRset.

\item \var{val\_rrset\_section}\verb" "

Section in which the RRset was received.  This may be one of the following:
\begin{itemize}
\item \const{VAL\_FROM\_ANSWER}
\item \const{VAL\_FROM\_AUTHORITY}
\item \const{VAL\_FROM\_ADDITIONAL}
\end{itemize}

\item \var{val\_rrset\_data}\verb" "

Response RDATA.

\item \var{val\_rrset\_sig}\verb" "

Any associated RRSIGs for the RDATA returned in \var{val\_rrset\_data}.

\end{description}

\item \struct{struct rr\_rec}\verb" "

\begin{verbatim}
    struct rr_rec
    {
        u_int16_t        rr_rdata_length_h;  
        u_int8_t        *rr_rdata;      
        val_astatus_t    rr_status;
        struct rr_rec   *rr_next;
    };
\end{verbatim}

\begin{description}

\item \var{rr\_rdata\_length\_h}\verb" "

Length of data stored in \var{rr\_rdata}.

\item \var{rr\_rdata}\verb" "

RDATA bytes.

\item \var{rr\_status}\verb" "

For each signature \var{rr\_rec} member within the authentication chain
\var{val\_ac\_rrset}, the validation status stored in the variable
\var{rr\_status} can return one of the following values:

\begin{itemize}

\item \const{VAL\_AC\_RRSIG\_VERIFIED}\verb" "

The RRSIG verified successfully.

\item \const{VAL\_AC\_WCARD\_VERIFIED}\verb" "

A given RRSIG covering a resource record shows that the record was wildcard
expanded.

\item \const{VAL\_AC\_RRSIG\_VERIFY\_FAILED}\verb" "

A given RRSIG covering an RRset was bogus.

\item \const{VAL\_AC\_DNSKEY\_NOMATCH}\verb" "

An RRSIG was created by a DNSKEY that did not exist in the apex keyset.

\item \const{VAL\_AC\_RRSIG\_ALGORITHM\_MISMATCH}\verb" "

The keytag referenced in the RRSIG matched a DNSKEY but the algorithms were
different.

\item \const{VAL\_AC\_WRONG\_LABEL\_COUNT}\verb" "

The number of labels on the signature was greater than the count given in
the RRSIG RDATA.

\item \const{VAL\_AC\_BAD\_DELEGATION}\verb" "

An RRSIG was created with a key that did not exist in the parent DS record
set.

\item \const{VAL\_AC\_RRSIG\_NOTYETACTIVE}\verb" "

The RRSIG's inception time is in the future.

\item \const{VAL\_AC\_RRSIG\_EXPIRED}\verb" "

The RRSIG had expired.

\item \const{VAL\_AC\_INVALID\_RRSIG}\verb" "

The RRSIG could not be parsed.

\item \const{VAL\_AC\_ALGORITHM\_NOT\_SUPPORTED}\verb" "

The RRSIG algorithm was not supported.

\item \const{VAL\_AC\_UNKNOWN\_ALGORITHM}\verb" "

The RRSIG algorithm was unknown.

\item \const{VAL\_AC\_ALGORITHM\_REFUSED}\verb" "

The RRSIG algorithm was not allowed as per local policy.

\end{itemize}

For each \var{rr\_rec} member of type DNSKEY (or DS, where relevant) within the
authentication chain \var{val\_ac\_rrset}, the validation status is stored in
the variable \var{rr\_status} and can return one of the following values:

\begin{itemize}

\item \const{VAL\_AC\_SIGNING\_KEY}\verb" "

This DNSKEY was used to create an RRSIG for the resource record set.

\item \const{VAL\_AC\_VERIFIED\_LINK}\verb" "

This DNSKEY provided the link in the authentication chain from the trust
anchor to the signed record.

\item \const{VAL\_AC\_UNKNOWN\_ALGORITHM\_LINK}\verb" "

This DNSKEY provided the link in the authentication chain from the trust
anchor to the signed record, but the DNSKEY algorithm was unknown.

\item \const{VAL\_AC\_INVALID\_KEY}\verb" "

The key used to verify the RRSIG was not a valid DNSKEY.

\item \const{VAL\_AC\_KEY\_TOO\_LARGE}\verb" "

Local policy defined the DNSKEY size as being too large.

\item \const{VAL\_AC\_KEY\_TOO\_SMALL}\verb" "

Local policy defined the DNSKEY size as being too small.

\item \const{VAL\_AC\_KEY\_NOT\_AUTHORIZED}\verb" "

Local policy defined the DNSKEY to be unauthorized for validation.

\item \const{VAL\_AC\_ALGORITHM\_NOT\_SUPPORTED}\verb" "

The DNSKEY or DS algorithm was not supported.

\item \const{VAL\_AC\_UNKNOWN\_ALGORITHM}\verb" "

The DNSKEY or DS algorithm was unknown.

\item \const{VAL\_AC\_ALGORITHM\_REFUSED}\verb" "

The DNSKEY or DS algorithm was not allowed as per local policy.

\end{itemize}

% \end{description}

\item \var{rr\_next}\verb" "

Points to the next resource record in the RRset.

\end{description}

\end{description}

{\bf RETURN VALUES}

Return values for \func{val\_resolve\_n\_check()} and
\func{val\_create\_context()} are given below.

\begin{description}

\item \func{val\_resolve\_n\_check()}

\begin{description}

\item \const{VAL\_NO\_ERROR} - No error was encountered.

\item \const{VAL\_GENERIC\_ERROR} - Generic error encountered.

\item \const{VAL\_NOT\_IMPLEMENTED} - Functionality not yet implemented.

\item \const{VAL\_BAD\_ARGUMENT} - Bad arguments passed as parameters.

\item \const{VAL\_INTERNAL\_ERROR} - Encountered some internal error.

\item \const{VAL\_NO\_PERMISSION} - No permission to perform operation.
Currently not implemented.

\item \const{VAL\_RESOURCE\_UNAVAILABLE} - Some resource (crypto possibly) was
unavailable.  Currently not implemented.

\end{description}

\item \func{val\_create\_context()}

\begin{description}

\item \const{VAL\_NO\_ERROR} - No error was encountered.

\item \const{VAL\_RESOURCE\_UNAVAILABLE} - Could not allocate memory.

\item \const{VAL\_CONF\_PARSE\_ERROR} - Error in parsing some configuration
file.

\item \const{VAL\_CONF\_NOT\_FOUND} - A configuration file was not available.

\item \const{VAL\_NO\_POLICY} - The policy identifier being referenced was
invalid.

\end{description}

\end{description}

{\bf FILES}

The validator library reads configuration information from two files,
\path{/etc/resolv.conf} and \path{/etc/dnsval.conf}.

Only the ``nameserver'' option is supported in the \path{resolv.conf} file.
This option is used to specify the IP address of the name server to which
queries must be sent by default.  For example,

\begin{verbatim}
    nameserver 10.0.0.1
\end{verbatim}

See \path{dnsval.conf(5)} for a description of the validator configuration file.

{\bf CURRENT STATUS}

There is currently no support for IPv6.

The caching functionality is very basic and no timeout logic currently exists.

There are a number of feature enhancements that still remain to be done.

{\bf SEE ALSO}

\lib{libsres(3)}

\path{dnsval.conf(5)}
