\clearpage

\subsubsection{\bf TrustMan}

{\bf NAME}

\cmd{TrustMan} - manage keys used as trust anchors

{\bf SYNOPSIS}

\begin{verbatim}
    TrustMan [options]
\end{verbatim}

{\bf DESCRIPTION}

\cmd{TrustMan} runs by default as a daemon to verify if keys stored locally in
configuration files like \path{named.conf} still match the same keys as fetched
from the zone where they are defined.  If mismatches are detected, the daemon
notifies via email the contact person defined in the DNSSEC-Tools
configuration file or on the command line.

\cmd{TrustMan} can also be run in the foreground ({\it -f}) to run this check
a single time.

\cmd{TrustMan} can also be used to set up configuration data in the file
\path{dnssec-tools.conf} for later use by the daemon, making fewer command
line arguments necessary.  Configuration data are stored in
\path{dnssec-tools.conf}.  The current version requires the
\path{dnssec-tools.conf} file to be edited by hand to add values for the
contact person's email address ({\it tacontact}) and the SMTP server ({\it
tasmtpserver}).  Also, the location of \path{named.conf} and
\path{dnsval.conf} must also be added to that file, if necessary.

{\bf OPTIONS}

\begin{description}

\item -f\verb" "

Run in the foreground.

\item -c\verb" "

Create a configure file for \cmd{TrustMan} from the command line options given.

\item -o\verb" "

Output file for configuration.

\item -k \verb" "

A \path{dnsval.conf} file to read.

\item -n \verb" "

A \path{named.conf} file to read.

\item -d\verb" "

The domain to check (supersedes configuration file.)

\item -t\verb" "

The number of seconds to sleep between checks.  Default is 3600 (one hour.)

\item -m\verb" "

Mail address for the contact person to whom reports should be sent.

\item -p\verb" "

Log messages to {\it stdout}.

\item -L\verb" "

Log messages to {\bf syslog}.

\item -s\verb" "

SMTP server \cmd{TrustMan} should use to send reports.

\item -N\verb" "

Send report when there are no errors.

\item -v\verb" "

Verbose.

\end{description}

{\bf SEE ALSO}

\path{dnssec-tools.conf(5)},
\path{dnsval.conf(5)},
\path{named.conf(5)}

