\clearpage

\subsubsection{\bf blinkenlights}

{\bf NAME}

\cmd{blinkenlights} - DNSSEC-Tools \cmd{rollerd} GUI

{\bf SYNOPSIS}

\begin{verbatim}
    blinkenlights <rollrec-file>
\end{verbatim}

{\bf DESCRIPTION}

\cmd{blinkenlights} is a GUI tool for use with monitoring and controlling the
DNSSEC-Tools \cmd{rollerd} program.  It displays information on the current
state of the zones \cmd{rollerd} is managing.  The user may control some
aspects of \cmd{rollerd}'s execution using \cmd{blinkenlights} menu commands.

\cmd{blinkenlights} creates a window in which to display information about
each zone \cmd{rollerd} is managing.  (These zones are those in {\bf
rollerd}'s current {\it rollrec} file.) As a zone's rollover status changes,
\cmd{blinkenlights} will update its display for that zone.  Skipped zones,
zones listed in the {\it rollrec} file but which are not in rollover or normal
operation, are displayed but have very little useful information to display.

The user may also select a set of zones to hide from the display.  These
zones, if in the rolling state, will continue to roll; however, their zone
information will not be displayed.  Display state for each zone will persist
across \cmd{blinkenlights} executions.

Menu commands are available for controlling \cmd{rollerd}.  The commands which
operate on a single zone may be executed by keyboard shortcuts.  The zone may
be selected either by clicking in its ``zone stripe'' or by choosing from a
dialog box.  Display and execution options for \cmd{blinkenlights} are also
available through menu commands.  More information about the menu commands is
available in the {\bf MENU COMMANDS} section.

\cmd{blinkenlights} is only intended to be started by \cmd{rollerd}, not
directly by a user.  There are two ways to have \cmd{rollerd} start
\cmd{blinkenlights}.  First, \cmd{rollctl} may be given the {\it -display}
option.  Second, the {\it -display} option may be given on \cmd{rollerd}'s
command line.

{\bf SCREEN LAYOUT}

The \cmd{blinkenlights} window is laid out as a series of ``stripes''.  The top
stripe contains status information about \cmd{rollerd}, the second stripe
contains column headers, and the bulk of the window consists of zone stripes.
The list below provides more detail on the contents of each stripe.

See the {\bf WINDOW COLORS} section for a discussion of the colors used for
the zone stripes.

\begin{description}

\item {\it \cmd{rollerd} information stripe}\verb" "

The information stripe contains four pieces of information:  \cmd{rollerd}'s
current {\it rollrec} file, the count of rolling zones, the count of skipped
zones, and the amount of time \cmd{rollerd} waits between processing its queue.
Coincidentally, that last datum is also the amount of time between
\cmd{blinkenlights} screen updates.

\item {\it column headers stripe}

This stripe contains the column headers for the columns of each zone stripe.

\item {\it zone stripes}

Each zone managed by \cmd{rollerd} (i.e., every zone in the current {\it
rollrec} file) will have a zone stripe which describes that zone's current
state.  The stripe is divided into three sections:  the zone name, the current
rollover state, and the zone's DNSSEC keys.

The zone name section just contains the name of the zone.

The rollover state section contains the rollover phase number, a text
explanation of the phase, and the amount of time remaining in that rollover
phase.  The phase explanation is ``normal operation'' when the zone isn't
currently in rollover.

The DNSSEC key section contains the names of the Current, Published, and New
ZSK keys for that stripe's zone.

See the {\bf WINDOW COLORS} section for a discussion of the colors used for
the zone stripes.

\end{description}

{\bf WINDOW COLORS}

The default \cmd{blinkenlights} configuration uses window coloring to provide
visual cues and to aid in easily distinguishing zone information.  The default
window coloring behavior gives each zone stripe has its own color and the
rollover state section of each zone stripe is shaded to show the zone's phase.
Window coloring can be turned off (and on) with configuration options and menu
commands.

The two window coloring behaviors are discussed more fully below:

\begin{description}

\item {\it zone stripe colors}

Each rolling zone's stripe is given one of three colors:  blue, red, or green.
The color is assigned on a top-down basis and the colors wrap if there are
more than three zones.  So, the first zone is always blue, the second zone
red, the third zone green, the fourth zone blue, etc.

The colors do not stay with a particular zone.  If a rolling zone becomes a
skipped zone, the zone stripes will be reassigned new colors to account for
that skipped zone.

Skipped zones are not colored with these three colors.  Stripes for skipped
zones are colored either grey or a color set in the configuration file.  If
you choose to use a non-standard color for skipped zones your should ensure
that it is {\bf not} one of the colors used for rolling zones' stripes.
Modifying the {\bf skipcolor} configuration field allows the skipped-zone color
to be changing.

The {\bf colors} configuration field can be used to turn on or off the use of
colors for zone stripes.  If stripe coloring is turned off, then every stripe
will be displayed using the {\bf skipcolor} color.

\item {\it rollover-state shading}

The only portion of a zone stripe that changes color is the status column; the
color of the rest of the zone stripe stays constant.  Before a zone enters
rollover, the status column is the same color as the rest of the stripe.  When
the zone enters rollover, the status column's color is changed to a very light
shade of the stripe's normal color.  As the rollover phases progress towards
rollover completion, the status column's shade darkens.  Once rollover
completes, the status column returns again to the same shade as the rest of
that stripe.

The {\bf shading} configuration field can be used to turn on or off the use of
shading in the rollover-state column.  If shading is turned off, then the zone
stripe will be a solid color.

See the {\bf CONFIGURATION FILE} section for information on setting the
configuration fields.

\end{description}

{\bf MENU COMMANDS}

A number of menu commands are available to control the behavior of
\cmd{blinkenlights} and to send commands to \cmd{rollerd}.  These commands
are discusses in this section.

{\bf File Menu}

The commands in this menu are basic GUI commands.

\begin{description}

\item {\it Quit}

\cmd{blinkenlights} will stop execution.

\end{description}

{\bf Options Menu}

The commands in this menu control the appearance and behavior of
\cmd{blinkenlights}.

\begin{description}

\item {\it Row Colors} (toggle)

This menu item is a toggle to turn on or off the coloring of zone stripes.
If row coloring is turned off, zone stripes will all be the same color.
If row coloring is turned on, zone stripes will be displayed in varying
colors.  See the {\bf WINDOW COLORS} section for a discussion of row coloring.

\item {\it Status Column Shading} (toggle)

This menu item is a toggle to turn on or off the shading of the zone status
column.  If shading is turned off, the zone stripes will present a solid,
unchanging band of color for each zone.  If shading is turned on, the color
of the zone status column will change according to the zone's rollover state.

\item {\it Skipped Zones Display} (toggle)

This menu item is a toggle to turn on or off the display of skipped zones.  If
display is turned off, zone stripes for skipped zones will not be displayed.
If display is turned on, zone stripes for all zones will be displayed.

\item {\it Modification Commands} (toggle)

In some situations, it may be desirable to turn off \cmd{blinkenlights}'
ability to send commands to \cmd{rollerd}.  This menu item is a toggle to turn
on or off this ability.  If the commands are turned off, then the ``Zone
Control'' menu and keyboard shortcuts are disabled.  If the commands are turned
on, then the ``Zone Control'' menu and keyboard shortcuts are enabled.

\item {\it Font Size}

This menu item allows selection of font size of text displayed in the main
window.

Normally, changing the font size causes the window to grow and shrink as
required.  However, on Mac OS X there seems to be a problem when the size
selected increases the window size to be greater than will fit on the screen.
If the font size is subsequently reduced, the window size does not shrink in
response.

\end{description}

{\bf Zone Control Menu}

The commands in this menu are GUI interfaces for the \cmd{rollctl} command.
Not all of the \cmd{rollctl} commands have interfaces -- only those which
directly affect zone management.

\begin{description}

\item {\it Roll Selected Zone}

The selected zone will be moved to the rollover state.  This only has an
effect on skipped zones.  A zone may be selected by clicking on its zone
stripe.  If this command is selected without a zone having been selected,
a dialog box is displayed from which a currently skipped zone may be chosen.

\item {\it Roll All Zones}

All zones will be moved to the rollover state.  This has no effect on
currently rolling zones.

\item {\it Run the Queue}

\cmd{rollerd} is awoken and runs through its queue of zones.  The operation
required for each zone is then performed.

\item {\it Skip Selected Zone}

The selected zone will be moved to the skipped state.  This only has an effect
on rolling zones.  A zone may be selected by clicking on its zone stripe.  If
this command is selected without a zone having been selected, a dialog box is
displayed from which a currently rolling zone may be chosen.

\item {\it Skip All Zones}

All zones will be moved to the skipped state.  This has no effect on
currently skipped zones.

\item {\it Halt Rollerd}

\cmd{rollerd}'s execution is halted.  As a result, \cmd{blinkenlights}'
execution will also be halted.

\end{description}

{\bf Zone Display Menu}

The commands in this menu are GUI interfaces for displaying or hiding zone
stripes.  The commands allow all, some, or none of the zone stripes to be
displayed.  Undisplayed rolling zones will continue to roll, but they will
do so without the \cmd{blinkenlights} window indicating this.

\begin{description}

\item {\it Zone Selection}

A dialog box is created that holds a list of the zones currently managed by
\cmd{rollerd}.  The user may select which zones should be displayed by clicking
on the zone's checkbox.  Zones with a selected checkbox will be displayed;
zones without a selected checkbox will not be displayed.

\item {\it Display All Zones}

All zones will be displayed in the \cmd{blinkenlights} window.

\item {\it Hide All Zones}

No zones will be displayed in the \cmd{blinkenlights} window.

\end{description}

{\bf Help Menu}

The commands in this menu provide assistance to the user.

\begin{description}

\item {\it Help}

Display a window containing help information.

\end{description}

{\bf CONFIGURATION FILE}

Several aspects of \cmd{blinkenlights}' behavior may be controlled from
configuration files.  Configuration value may be specified in the DNSSEC Tools
configuration file or in a more specific \path{rc.blinkenlights}.  The
system-wide \cmd{blinkenlights} configuration file is in the DNSSEC-Tools
configuration directory and is named \path{blinkenlights.conf}.  Multiple
\path{rc.blinkenlights} files may exist on a system, but only one in the
directory in which \cmd{blinkenlights} is executed is used.

The following are the available configuration values:

\begin{verbatim}
    colors         Turn on/off use of colors on zone stripes
    fontsize       The size of the font in the output window
    modify         Turn on/off execution of rollerd modification commands
    shading        Turn on/off shading of the status columns
    showskip       Turn on/off display of skipped zones
    skipcolor      The background color used for skipped zones
\end{verbatim}

The \path{rc.blinkenlights} file is {\bf only} searched for in the directory in
which \cmd{blinkenlights} is executed.  The potential problems inherent in
this may cause these \cmd{blinkenlights}-specific configuration files to be
removed in the future.

This file is in the ``field value'' format, where {\it field} specifies the
output aspect and {\it value} defines the value for that field.  The following
are the recognized fields:

Empty lines and comments are ignored.  Comment lines are lines that start
with an octothorpe (`\#').

Spaces are not allowed in the configuration values.

Choose your skipcolors carefully.  The only foreground color used is black, so
your background colors must work well with black.

{\bf REQUIREMENTS}

\cmd{blinkenlights} is implemented in Perl/Tk, so both Perl and Perl/Tk must be
installed on your system.

{\bf WARNINGS}

\cmd{blinkenlights} has several potential problems that must be taken into
account.

\begin{description}

\item [development environment]\verb" "

\cmd{blinkenlights} was developed and tested on a single-user system running
X11.  While it works fine in this environment, it has not been run on a system
with many users or in a situation where the system console hasn't been in use
by the \cmd{blinkenlights} user.

\item [long-term performance issues]\verb" "

In early tests, the longer \cmd{blinkenlights} runs, the slower the
updates become.  This is {\it probably} a result of the Tk implementation
or the way Tk interfaces with X11.  This is pure supposition, though.

This performance impact is affected by a number of things, such as the number
of zones managed by \cmd{rollerd} and the length of \cmd{rollerd}'s sleep
interval.  Large numbers of zones or very short sleep intervals will increase
the possibility of \cmd{blinkenlights}' performance degrading.

This appears to have been resolved by periodically performing a complete
rebuild of the screen.  \cmd{blinkenlights} keeps track of the number of
screen updates it makes and rebuilds the screen when this count exceeds a
threshold.  The threshold is built into \cmd{blinkenlights} and stored in the
{\bf \$PAINTMAX} variable.  This threshold may be adjusted if there are too
many screen rebuilds or if \cmd{blinkenlights}' performance slows too much.
Raising the number will reduce the screen rebuilds; lowering the number will
(may) increase performance.

\end{description}

{\bf SEE ALSO}

\cmd{rollctl(8)},
\cmd{rollerd(8)},
\cmd{zonesigner(8)}

\perlmod{Net::DNS::SEC::Tools::timetrans.pm(3)}

\path{keyrec(5)},
\path{rollrec(5)}
