\clearpage

\subsubsection{\bf rollchk}

{\bf NAME}

\cmd{rollchk} - Check a DNSSEC-Tools {\it rollrec} file for problems and
inconsistencies.

{\bf SYNOPSIS}

\begin{verbatim}
    rollchk [-roll|-skip] [-count] [-quiet] [-verbose] [-help] rollrec-file
\end{verbatim}

{\bf DESCRIPTION}

This script checks the {\it rollrec} file specified by {\it rollrec-file} for
problems and inconsistencies.

Recognized problems include:

\begin{description}

\item {\it non-existent rollrec file}\verb" "

The specified {\it rollrec} file does not exist.

\item {\it no zones defined}\verb" "

No zones are defined in the specified {\it rollrec} file.

\item {\it invalid rollover phase}\verb" "

A zone has an invalid rollover phase.  These phases may be 0, 1, 2, 3, or 4;
any other value is invalid.

\item {\it invalid display flag}\verb" "

A zone has an invalid display flag.  This flag may be 0 or 1;
any other value is invalid.

\item {\it non-positive maxttl}\verb" "

The maximum TTL value must be greater than zero.

\item {\it zone file checks}\verb" "

Several checks are made for a zone's zone file.  The zone file must exist, it
must be a regular file, and it must not be of zero length.

\item {\it keyrec file checks}\verb" "

Several checks are made for a zone's {\it keyrec} file.  The {\it keyrec} file
must exist, it must be a regular file, and it must not be of zero length.

\end{description}

{\bf OPTIONS}

\begin{description}

\item {\it -roll}\verb" "

Only display {\it rollrec}s that are active (``roll'') records.
This option is mutually exclusive of the {\it -skip} option.

\item {\it -skip}\verb" "

Only display {\it rollrec}s that are inactive (``skip'') records.
This option is mutually exclusive of the {\it -roll} option.

\item {\it -count}\verb" "

Display a final count of errors.

\item {\it -quiet}\verb" "

Do not display messages.  This option supersedes the setting of the {\it -v}
option.

\item {\it -verbose}\verb" "

Display many messages.  This option is subordinate to the {\it -q} option.

\item {\it -help}\verb" "

Display a usage message.

\end{description}


{\bf SEE ALSO}

\cmd{lsroll(8)},
\cmd{rollerd(8)},
\cmd{rollinit(8)}

\perlmod{Net::DNS::SEC::Tools::rollrec.pm(3)}

\path{rollrec(5)}
