\clearpage

\subsubsection{\bf getdnskeys}

{\bf NAME}

\cmd{getdnskeys} - Manage lists of DNSKEYs from DNS zones.

{\bf SYNOPSIS}

\begin{verbatim}
    getdnskeys [-i file] [-o file] [-k] [-T] [-t] [-v] [zones]
\end{verbatim}

{\bf DESCRIPTION}

\cmd{getdnskeys} manages lists of DNSKEYs from DNS zones.  It may be used to
retrieve and compare DNSKEYs.  The output from \cmd{getdnskeys} may be
included (directly or indirectly) in a \path{named.conf} file.

{\bf OPTIONS}

\begin{description}

\item {\it -h}\verb" "

Gives a help message.

\item {\it -i path}\verb" "

Reads {\it path} as a \path{named.conf} with which to compare key lists.

\item {\it -k}\verb" "

Only looks for Key Signing Keys (KSK); all other keys are ignored.

\item {\it -o file}\verb" "

Writes the results to {\it file}.

\item {\it -T}\verb" "

Checks the current trusted key list from \path{named.conf}.

\item {\it -t}\verb" "

Encloses output in needed \path{named.conf} syntax markers.

\item {\it -v}\verb" "

Turns on verbose mode for additional output.

\end{description}

{\bf EXAMPLES}

This \cmd{getdnskeys} will retrieve the KSK for example.com:

\begin{verbatim}
    getdnskeys -o /etc/named.trustkeys.conf -k -v -t example.com
\end{verbatim}

This \cmd{getdnskeys} will check saved keys against a live set of keys:

\begin{verbatim}
    getdnskeys -i /etc/named.trustkeys.conf -T -k -v -t
\end{verbatim}

This \cmd{getdnskeys} will automatically update a set of saved keys:

\begin{verbatim}
    getdnskeys -i /etc/named.trustkeys.conf -k -t -T -v   \
               -o /etc/named.trustkeys.conf
\end{verbatim}

{\bf SECURITY ISSUES}

Currently this does not validate new keys placed in the file in any
way, nor does it validate change over keys which have been added.

It also does not handle revocation of keys.

It should prompt you before adding a new key so that you can always
run the auto-update feature.
