\clearpage

\subsection{\bf BootStrap.pm Module}

{\bf NAME}

\perlmod{Net::DNS::SEC::Tools::BootStrap.pm} - Optional loading of Perl modules

{\bf SYNOPSIS}

\begin{verbatim}
    use Net::DNS::SEC::Tools::BootStrap;

    dnssec_tools_load_mods(PerlModule => 'Additional help/error text');
\end{verbatim}


{\bf DESCRIPTION}

The DNSSEC-Tools package requires a number of Perl modules that are only
needed by some of the tools.  This module helps determine at run-time, rather
than at installation time, if the right tools are available on the system.
If any module fails to load, \func{dnssec\_tools\_load\_mods()} will display an
error message and calls \sys{exit()}.  The error message describes how to
install a module via CPAN.

The arguments to \func{dnssec\_tools\_load\_mods()} are given in pairs.  Each
pair is a module to try to load (and import) and an supplemental error
message.  If the module fails to load, the supplemental error message will be
displayed along with the installation-via-CPAN message.  If the error message
consists of the string ``noerror'', then no error message will be displayed
before the function exits.

{\bf CAVEATS}

The module will try to import any exported subroutines from the module into
the {\it main} namespace.  This means that the \perlmod{BootStrap.pm} module
is likely not useful for importing symbols into other modules.  Work-arounds
for this are:

\begin{description}

\item {\it import the symbols by hand}\verb" "

\begin{verbatim}
    dnssec_tools_load_mods(PerlModule => 'Additional help/error text');

    import PerlModule qw(func1 func2);

    func1(arg1, arg2);
\end{verbatim}

\item {\it call the fully qualified function names}\verb" "

\begin{verbatim}
    dnssec_tools_load_mods(PerlModule => 'Additional help/error text');

    PerlModule::func1(arg1, arg2);
\end{verbatim}

\end{description}
