\clearpage

\subsubsection{rollset}

{\bf NAME}

\cmd{rollset} - Modifies entries in a DNSSEC-Tools \struct{rollrec} file

{\bf SYNOPSIS}

\begin{verbatim}

  rollset [options] rollrec-file

\end{verbatim}

{\bf DESCRIPTION}

\cmd{rollset} modifies fields in the \struct{rollrec} file specified
by {\it rollrec-file}.  Multiple options may be combined in a single
\cmd{rollset} execution.  \cmd{rollset} operates quietly unless it is
given the {\it -verbose} option.

All records in the specified \struct{rollrec} file will be modified, unless
the {\it -zone} option is given.  In that case, only the named zone will be
modified.

{\bf OPTIONS}

\begin{description}

\item {\bf -zone zonename}\verb" "

The zone {\it zonename} is selected as the only zone whose \struct{rollrec}
record will be modified.  If this is not given, then all \struct{rollrec}
records will be modified.

\item {\bf -file zone-file}\verb" "

The zone file in the selected \struct{rollrec} records is modified to be
{\it zone-file}.

\item {\bf -keyrec keyrec-file}\verb" "

The keyrec file in the selected \struct{rollrec} records is modified to be
{\it keyrec-file}.

\item {\bf -admin addr}\verb" "

The zone administrator's email address is set to {\it addr}.

\item {\bf -del-admin}\verb" "

The {\it administrator} line is deleted.

\item {\bf -del-directory}\verb" "

The {\it directory} line is deleted.

\item {\bf -del-loglevel}\verb" "

The {\it loglevel} line is deleted.

\item {\bf -directory dir}\verb" "

The directory to hold the zone's files is set to {\it dir}.

\item {\bf -loglevel logging-level}\verb" "

The logging level of the selected \struct{rollrec} records is set to
{\it logging-level}.  The valid logging levels are defined in
\perlmod{rollmgr.pm(3)}.

\item {\bf -display}\verb" "

Turn on the GUI display of the zones in the selected \struct{rollrec}s.
This option is mutually exclusive of the {\it -nodisplay} option.

\item {\bf -nodisplay}\verb" "

Turn off the GUI display of the zones in the selected \struct{rollrec}s.
This option is mutually exclusive of the {\it -display} option.

\item {\bf -roll}\verb" "

Convert the selected \struct{rollrec}s to be active (``roll'') records.
This option is mutually exclusive of the {\it -skip} option.

\item {\bf -skip}\verb" "

Convert the selected \struct{rollrec}s to be inactive (``skip'') records.
This option is mutually exclusive of the {\it -roll} option.

\item {\bf -check}\verb" "

If this option is given, the \cmd{rollchk} command will be run on the modified
\struct{rollrec} file.

\item {\bf -verbose}\verb" "

Display information about every modification made to the \struct{rollrec} file.

\item {\bf -Version}\verb" "

Display the current \cmd{rollset} and DNSSEC-Tools versions.

\item {\bf -help}\verb" "

Display a usage message.

\end{description}

{\bf SEE ALSO}

lsroll(8),
rollchk(8),
rollerd(8),
rollinit(8)

Net::DNS::SEC::Tools::rollmgr.pm(3),
Net::DNS::SEC::Tools::rollrec.pm(3)

file-rollrec(5)

