\clearpage

\subsubsection{\bf timetrans}

{\bf NAME}

\cmd{timetrans} - Converts time into time.

{\bf SYNOPSIS}

\begin{verbatim}
    timetrans [units-options] [-count]
\end{verbatim}

{\bf DESCRIPTION}

{\it timetrans} converts time from one type of unit to another.  If any of the
units options are specified, then {\it timetrans} will convert those time units
into the number of seconds to which they add up.  If given the count option,
{\it timetrans} will convert that number of seconds into the appropriate number
of weeks, days, hours, minutes, and seconds.  The converted result is printed
out.  Units options cannot be specified in the same execution as the count
option, and vice versa.

{\it timetrans} is intended for use with DNSSEC-Tools, for calculating
a zone's expiration time.

{\bf OPTIONS}

{\bf Units Options}

The converted value of each unit is totaled and a single result printed.
These options may be shortened to their first letter.

\begin{description}

\item {\it -seconds seconds}\verb" "

Count of seconds to convert to seconds.

\item {\it -minutes minutes}\verb" "

Count of minutes to convert to seconds.

\item {\it -hours hours}\verb" "

Count of hours to convert to seconds.

\item {\it -days days}\verb" "

Count of days to convert to seconds.

\item {\it -weeks weeks}\verb" "

Count of weeks to convert to seconds.

\end{description}

{\bf Count Option}

The specified seconds count is converted to the appropriate number of weeks,
days, hours, minutes, and seconds.  This option may be shortened to its first
letter.

\begin{description}

\item {\it -count seconds}\verb" "

Count of seconds to convert to the appropriate set of units.

\end{description}

{\bf EXAMPLES}

Example 1:  Converting 5 days into seconds

\begin{verbatim}
    $(42)> timetrans -days 5
    432000
\end{verbatim}

Example 2:  Converting 2 weeks into seconds

\begin{verbatim}
    $(43)> timetrans -w 2
    1209600
\end{verbatim}

Example 3:  Converting 8 days and 8 hours into seconds

\begin{verbatim}
    $(44)> timetrans -d 8 -hours 8
    720000
\end{verbatim}

Example 4:  Converting 1 week, 1 day, and 8 hours into seconds

\begin{verbatim}
    $(46)> timetrans -w 1 -days 1 -h 8
    720000
\end{verbatim}

Example 5:  Converting 14 weeks, 4 days, 21 hours, 8 minutes, and 8 seconds into seconds

\begin{verbatim}
    $(47)> timetrans -w 14 -d 4 -h 21 -m 8 -s 8
    8888888
\end{verbatim}

Example 6:  Converting 720000 seconds into time units

\begin{verbatim}
    $(48)> timetrans -c 720000
    1 week, 1 day, 8 hours
\end{verbatim}

Example 7:  Converting 1814421 seconds into time units

\begin{verbatim}
    $(49)> timetrans -c 1814421
    3 weeks, 21 seconds
\end{verbatim}

Example 8:  Converting 8888888 seconds into time units

\begin{verbatim}
    $(50)> timetrans -c 8888888
    14 weeks, 4 days, 21 hours, 8 minutes, 8 seconds
\end{verbatim}


{\bf SEE ALSO}

\cmd{zonesigner(8)}

\perlmod{Net::DNS::SEC::Tools::timetrans.pm(3)}
