\clearpage

\subsubsection{dnssectools.pm}

{\bf NAME}

\perlmod{Net::DNS::SEC::Tools::dnssectools} - General routines for the
DNSSEC-Tools package.

{\bf SYNOPSIS}

\begin{verbatim}
  use Net::DNS::SEC::Tools::dnssectools;

  dt_adminmail($subject,$msgbody,$recipient);

  $zspath = dt_cmdpath('zonesigner');

  $ftype = dt_findtype($path);
\end{verbatim}

{\bf DESCRIPTION}

The \perlmod{dnssectools} module provides a general set of methods for use
with DNSSEC-Tools utilities.

{\bf INTERFACES}

The interfaces to the \perlmod{dnssectools} module are given below.

\begin{description}

\item \func{dt\_adminmail(subject,msgbody,recipient)}\verb" "

This routine emails a message to the administrative user listed in the
DNSSEC-Tools configuration file.

\func{dt\_adminmail()} requires two parameters, both scalars.
The \var{subject} parameter is the subject for the mail message.
The \var{msgbody} parameter is the body of the mail message.

A third parameter, \var{recipient}, may be given to specify the message's
recipient.  If this is not given, then the recipient will be taken from
the \var{admin-email} record of the DNSSEC-Tools configuration file.

Return values:

\begin{itemize}

\item 1 - the message was created and sent.
\item 0 - an invalid recipient was specified. 

\end{itemize}

\item \func{dt\_cmdpath(command)}\verb" "

This routine returns the path to a specified DNSSEC-Tools command.
\var{command} should be the name only, without any leading directories.
The command name is checked to ensure that it is a valid DNSEC-Tools command,

Return values:

\begin{itemize}

\item The absolute path to the command is returned if the command is valid.
\item Null is returned if the command is not valid.

\end{itemize}

\item \func{dt\_filetype(path)}\verb" "

This routine returns the type of the file named in \var{path}.  The
\struct{rollrec} and \struct{keyrec} records contained therein are
counted and a type determination is made.

Return values:

\begin{description}

\item {\it keyrec}\verb" "

At least one \struct{keyrec} record was found and no \struct{rollrec} records
were found.

\item {\it rollrec}\verb" "

At least one \struct{rollrec} record was found and no \struct{keyrec} records
were found.

\item {\it mixed}\verb" "

At least one \struct{rollrec} record and at least one \struct{keyrec} record
were found.  This is most likely an erroneous file.

\item {\it unknown}\verb" "

No \struct{rollrec} records nor \struct{keyrec} records were found.

\item {\it nofile}\verb" "

The specified file does not exist.

\end{description}

\end{description}

{\bf SEE ALSO}

Mail::Send.pm(3),
Net::DNS::SEC::Tools::conf.pm(3)

