\clearpage

\subsubsection{val\_query()}

{\bf NAME}

\func{val\_query()}, \func{val\_res\_query()}, \func{val\_res\_search()} -
DNSSEC-validated resolution of DNS queries

{\bf SYNOPSIS}

\begin{verbatim}
    #include <validator.h>

    int val_query(const val_context_t *ctx,
                  const char *dname,
                  const u_int16_t class,
                  const u_int16_t type,
                  const u_int8_t flags,
                  struct val_response **resp);

    int val_free_response(struct val_response *resp);

    int val_res_query(const val_context_t *ctx,
                      const char *dname,
                      int class,
                      int type,
                      u_char *answer,
                      int anslen,
                      val_status_t *val_status);

    int val_res_search(val_context_t * ctx,
                       const char *dname,
                       int class_h,
                       int type,
                       u_char * answer,
                       int anslen,
                       val_status_t * val_status);
\end{verbatim}

{\bf DESCRIPTION}

The \func{val\_query()} and  \func{val\_res\_query()} functions perform DNSSEC
validation of DNS queries.  They are DNSSEC-aware substitutes for
\func{res\_query(3)}.  \func{val\_res\_search()} is a DNSSEC-aware substitute
for the \func{res\_search(3)} function.

The \var{ctx} parameter is the validator context and can be set to NULL for
default settings.  More information about this field can be found in
\lib{libval(3)}.

The \var{dname} parameter specifies the domain name, \var{class} specifies the
DNS class and \var{type} specifies the DNS type.

The \func{val\_query()} function returns results in the \var{resp} linked list
which encapsulates the results into the following structure:

\begin{verbatim}
    struct val_response
    {
          unsigned char *vr_response;
          int vr_length;
          val_status_t vr_val_status;
          struct val_response *vr_next;
    };
\end{verbatim}

The \var{vr\_response} and \var{vr\_length} fields are functionally similar to
the \var{answer} and \var{anslen} parameters in \func{res\_query(3)}.  Memory
for the \var{resp} linked list is internally allocated and must be released
after a successful invocation of the function using the
\func{val\_free\_response()} function.  Each element in the \var{resp} linked
list will contain an answer corresponding to a single RRSet in the DNS reply.

The validation status is returned in the \var{vr\_val\_status} field of the
\var{val\_response} structure for that RRSet.  \func{p\_val\_status()} returns
a brief string description of the error code.  \func{val\_istrusted()}
determines if the status code indicates that the response can be trusted and
\func{val\_isvalidated()} determines if the status code indicates that the
response was validated.  (See \lib{libval(3)} for further information).

The \var{flags} parameter controls the scope of validation and name
resolution, and the output format.  Three values, which may be ORed together,
are currently defined for this field.  The \const{VAL\_QUERY\_MERGE\_RRSETS}
flag is provided for applications that wish to merge all rrsets into a single
response returned in the first element of the \var{resp} array.  The response
field of this element will have a format similar to the answer returned by
\func{res\_query(3)}.  The \const{VAL\_QUERY\_DONT\_VALIDATE} flag causes the
validator to disable validation for this query, and the
\const{VAL\_QUERY\_NO\_DLV} flag causes the validator to disable DLV
processing for this query.  The last flag is only available if the
\lib{libval(3)} library has been compiled with DLV support.

\func{val\_res\_query()} is provided as a closer substitute for
\func{res\_query(3)}.  It calls \func{val\_query()} internally with the
\const{VAL\_QUERY\_MERGE\_RRSETS} flag and returns the answers in the field
answer with length of \var{anslen}.

\func{val\_res\_search()} performs an operation similar to
\func{val\_res\_query()}.  In addition, it uses the search paths specified
within the \path{/etc/resolv.conf} file to create the fully qualified domain
name.

The validation status values for \func{val\_res\_query()} and
\func{val\_res\_search()} functions are returned in their respective
\var{val\_status} fields.

{\bf RETURN VALUES}

The \func{val\_query()} function returns 0 on success.  It invokes
\func{resolve\_n\_check()} internally and errors from this function may be
returned.

\func{val\_res\_query()} and \func{val\_res\_search()} return the number of
bytes received on success and -1 on failure.

{\bf EXAMPLES}

\begin{verbatim}
    #include <stdio.h>
    #include <stdlib.h>
    #include <strings.h>
    #include <arpa/nameser.h>
    #include <validator.h>

    #define BUFLEN 8096
    #define RESPCOUNT 3

    int main(int argc, char *argv[])
    {
             int retval;
             int i;
             int class = ns_c_in;
             int type = ns_t_a;
             struct val_response *resp, *iter;

             if (argc < 2) {
                 printf("Usage: %s <domain-name>\n", argv[0]);
                 exit(1);
             }

             retval = val_query(NULL, argv[1], class, type, 0, &resp);

             if (retval == 0) {
                 for (iter=resp; iter; iter=iter->vr_next) {
                      printf("Validation Status = %d [%s]\n",
                              iter->vr_val_status,
                              p_val_status(iter->vr_val_status));
                     }
             }

             free_val_response(resp);

             return 0;
    }
\end{verbatim}

{\bf SEE ALSO}

res\_query(3)

get\_context(3), val\_getaddrinfo(3),
val\_gethostbyname(3)

libval(3)

