\clearpage

\subsubsection{val\_gethostbyname()}

{\bf NAME}

\func{val\_gethostbyname()}, \func{val\_gethostbyname2()},
\func{val\_gethostbyname\_r()}, \func{val\_gethostbyname2\_r()} -
get DNSSEC-validated network host entry

{\bf SYNOPSIS}

\begin{verbatim}
    #include <validator.h>

    extern int h_errno;
    struct hostent *val_gethostbyname(const val_context_t *ctx,
                                      const char *name,
                                      val_status_t *val_status);

    struct hostent *val_gethostbyname2(const val_context_t *ctx,
                                       const char *name,
                                       int af,
                                       val_status_t *val_status);

    int val_gethostbyname_r(const val_context_t *ctx,
                            const char *name,
                            struct hostent *ret,
                            char *buf,
                            size_t buflen,
                            struct hostent **result,
                            int *h_errnop,
                            val_status_t *val_status);

    int val_gethostbyname2_r(const val_context_t *ctx,
                             const char *name,
                             int af,
                             struct hostent *ret,
                             char *buf,
                             size_t buflen,
                             struct hostent **result,
                             int *h_errnop,
                             val_status_t *val_status);

      struct hostent *val_gethostbyaddr(val_context_t * ctx,
                                        const char *addr,
                                        int len,
                                        int type, 
                                        val_status_t * val_status);

      int val_gethostbyaddr_r(val_context_t * ctx,
                              const char *addr,
                              int len,
                              int type,
                              struct hostent *ret,
                              char *buf,
                              int buflen,
                              struct hostent **result,
                              int *h_errnop,
                              val_status_t * val_status);

\end{verbatim}

{\bf DESCRIPTION}

\func{val\_gethostbyname()}, \func{val\_gethostbyname2()},
\func{val\_gethostbyname\_r()}, \func{val\_gethostbyname2\_r()},
\func{val\_gethostbyaddr()} and \func{val\_gethostbyaddr\_r()}
perform DNSSEC validation of DNS queries.  They return a network host entry
value of type struct \struct{hostent} and are DNSSEC-aware versions of the
\func{gethostbyname(3)}, \func{gethostbyname2(3)}, \func{gethostbyname\_r()},
\func{gethostbyname2\_r()}, \func{gethostbyaddr()} and
\func{gethostbyaddr\_r()} functions respectively.  (See
\func{gethostbyname(3)} for more information on type struct \struct{hostent}).

\func{val\_gethostbyname()}, \func{val\_gethostbyname\_r()},
\func{val\_gethostbyaddr()}, and \func{val\_gethostbyaddr\_r()} support only
IPv4 addresses.
\func{val\_gethostbyname2()} and \func{val\_gethostbyname2\_r()} support both
IPv4 and IPv6 addresses.

The \func{val\_gethostbyname\_r()}, \func{val\_gethostbyname2\_r()} and
\func{val\_gethostbyaddr\_r()} functions are reentrant versions and can be
safely used in multi-threaded applications.

The \var{ctx} parameter specifies the validation context, which can be set to
NULL for default values (see \lib{libval(3)} and \path{dnsval.conf} for more
details on validation contexts and validation policy).

\func{val\_gethostbyname()}, \func{val\_gethostbyname2()} and
\func{val\_gethostbyaddr()} set the global \var{h\_errno} variable to return
the resolver error code.  The reentrant versions
\func{val\_gethostbyname\_r()}, \func{val\_gethostbyname2\_r()} and
\func{val\_gethostbyaddr\_r()} use the \var{h\_errnop} parameter to return
this value.  This ensures thread safety, by avoiding the global \var{h\_errno}
variable.  \var{h\_errnop} must not be NULL.  (See the man page for
\func{gethostbyname(3)} for possible values of \var{h\_errno}.)

The \var{name}, \var{af}, \var{ret}, \var{buf}, \var{buflen}, and \var{result}
parameters have the same syntax and semantics as the corresponding parameters
for the original \func{gethostbyname*()} and \func{gethostbyaddr*()}
functions.  See the manual page for \func{gethostbyname(3)} for more details
about these parameters.

The \var{val\_status} parameter is used to return the validator error code and
must not be NULL.  \func{val\_istrusted()} and \func{val\_isvalidated()} can
be used to determine the trustworthiness of data and \func{p\_val\_status()}
can be used to display the status value to the user in ASCII format (See
\lib{libval(3)} more for information).

{\bf RETURN VALUES}

The \func{val\_gethostbyname()}, \func{val\_gethostbyname2()}, and
\func{val\_gethostbyaddr()} functions return a pointer to a \struct{hostent}
structure when they can resolve the given host name (with or without DNSSEC
validation), and NULL if data was not available.  The memory for the returned
value is statically allocated by these two functions.  Hence, the caller must
not free the memory for the returned value.

The \func{val\_gethostbyname\_r()}, \func{val\_gethostbyname2\_r()} and
\func{val\_gethostbyaddr\_r()} functions return 0 when they can resolve the
given host name (with or without DNSSEC validation), and a non-zero error-code
on failure.

The \func{val\_gethostbyaddr()} and \func{val\_gethostbyaddr\_r()} functions
return 0 when they can resolve the given host name (with or without DNSSEC
validation), and a non-zero error-code on failure.

The \var{val\_status} parameter gives an indication for trustworthiness of
data. If the returned \struct{hostent} structure is NULL, this value gives an
indication of whether the non-existence of data can be trusted or not.

{\bf EXAMPLE}

\begin{verbatim}
    #include <stdio.h>
    #include <stdlib.h>
    #include <validator.h>

    int main(int argc, char *argv[])
    {
        int val_status;
        struct hostent *h = NULL;

        if (argc < 2) {
            printf("Usage: %s <hostname>\n", argv[0]);
            exit(1);
        }

        h = val_gethostbyname(NULL, argv[1], &val_status);
        printf("h_errno = %d [%s]\n", h_errno, hstrerror(h_errno));
        if (h) {
            printf("Validation Status = %d [%s]\n", val_status,
                   p_val_status(val_status));
        }

        return 0;
    }
\end{verbatim}

{\bf NOTES}

These functions do not currently read the order of lookup from
\path{/etc/hosts.conf}.  At present, the default order is set to consult the 
\path{/etc/hosts} file first and then query DNS.

The current versions of these functions do not support NIS lookups.

{\bf SEE ALSO}

gethostbyname(3),
gethostbyname2(3), 
gethostbyname\_r(3),
gethostbyname2\_r(3)

libval(3)

val\_getaddrinfo(3),
val\_query(3) 

