\clearpage

\subsubsection{libval\_check\_conf}

{\bf NAME}

\cmd{libval\_check\_conf} - command-line program for checking validity of
the validator configuration file

{\bf SYNOPSIS }

\begin{verbatim}
    libval_check_conf [options] <dnsval.conf>
\end{verbatim}

{\bf DESCRIPTION}

This program checks the validity of a given validator configuration file,
typically named \path{dnsval.conf}, for any syntax errors.  The input to this
program is a validator configuration file, but the program also requires valid
\path{resolv.conf} and \path{root.hints} to be specified.  The location for
these auxiliary files may be specified using the {\it -r} and {\it -i} options
respectively.  If these options are not provided, the default
\path{resolv.conf} and \path{root.hints} files recognized by the validator
library are used instead.  The program displays an error if the default
\path{resolv.conf} and \path{root.hints} files, and the {\it -i} and {\it -r}
are both unspecified.

{\bf RETURN VALUES}

The program returns 0 on success and -1 on failure.

{\bf OPTIONS}

\begin{description}

\item -r, --resolv-conf\verb" "

Specifies the location for the \path{resolv.conf} file.  If this option is not
specified the default \path{resolv.conf} file recognized by the validator
library is used instead.

\item -i, --root-hints\verb" "

Specifies the location for the \path{root.hints} file.  If this option is not
specified the default \path{root.hints} file recognized by the validator
library is used instead.

\item -v, --verbose\verb" "

Displays detailed messages and warnings associated with the validator
configuration file check process.

\item -h, --help\verb" "

Displays a usage help message and exits the program.

\end{description}

{\bf SEE ALSO}

dnsval.conf(3)

