
A number of commands have been developed to assist in maintaining
DNSSEC-secured domains.  These commands check zone files for errors,
assist in key generation and zone signing, perform key rollover, and
provide graphic information about zones.

The DNSSEC-Tools commands are divided in four functional groups:

\begin{itemize}

\item DNSSEC-Tools Maintenance Commands

\item DNS Zone-File Commands

\item Zone-Signing Commands

\item Key-Rollover Commands

\end{itemize}

The commands in each functional group are described in the following
subsections.

\clearpage
\subsection{\bf DNSSEC-Tools Maintenance Commands}
\label{ssect-cmds-maint}

The commands in this group primarily deal with DNSSEC-Tools configuration
file.  There is also a tool for time conversions, which may assist in
determining values for some fields for a zone.  The maintenance commands are:

\begin{table}[ht]
\begin{center}
\begin{tabular}{ll}
\cmd{dtinitconf} & create a new DNSSEC-Tools configuration file		\\
\cmd{dtdefs}	 & print the DNSSEC-Tools configuration values		\\
\cmd{dtconfchk}	 & checks a DNSSEC-Tools configuration file for errors	\\
\cmd{timetrans}	 & converts time units					\\
\end{tabular} 
\end{center}
\end{table}

\input{manpages/tools::scripts::dtinitconf.tex}
\input{manpages/tools::scripts::dtdefs.tex}
\input{manpages/tools::scripts::dtconfchk.tex}
\input{manpages/tools::scripts::timetrans.tex}

\clearpage
\subsection{\bf DNS Zone File Commands}
\label{ssect-cmds-zone}

The DNS zone file commands provide analytical and visualization tools for DNS
zone files.  These commands are:

\begin{table}[ht]
\begin{center}
\begin{tabular}{ll}
\cmd{dnspktflow} & analyzes and draw DNS flow diagrams			\\
\cmd{donuts}	 & analyzes DNS zone files for errors			\\
\cmd{donutsd}	 & daemon to periodically run \cmd{donuts}		\\
\cmd{getdnskeys} & manage lists of DNSKEYs from DNS zones		\\
\cmd{mapper}	 & creates maps of DNS zone data			\\
\cmd{TrustMan}	 & manage keys used as trust anchors			\\
\cmd{tachk}	 & verifies trust anchors in a \path{named.conf} file	\\
\cmd{validate}	 & query the Domain Name System 			\\
\end{tabular} 
\end{center}
\end{table}

\input{manpages/tools::dnspktflow::dnspktflow.tex}
\input{manpages/tools::donuts::donuts.tex}
\input{manpages/tools::donuts::donutsd.tex}
\input{manpages/tools::scripts::getdnskeys.tex}
\input{manpages/tools::mapper::mapper.tex}
\input{manpages/tools::scripts::TrustMan.tex}
\input{manpages/tools::scripts::tachk.tex}
\input{manpages/lib::libval::validate.tex}


\clearpage
\subsection{\bf Zone-Signing Commands}
\label{ssect-cmds-sign}

The zone-signing commands provide tools to assist in the signing DNS zone
files and keeping records about those signed zones.  These commands are:

\begin{table}[ht]
\begin{center}
\begin{tabular}{ll}
\cmd{zonesigner}	& generates encryption keys and signs a DNS zone \\
\cmd{genkrf}		& creates a new {\it keyrec} file		 \\
\cmd{krfcheck}		& checks a {\it keyrec} file for errors		 \\
\cmd{lskrf}		& lists the contents of a {\it keyrec} file	 \\
\cmd{expchk}		& checks a {\it keyrec} file for expired zones	 \\
\cmd{fixkrf}		& fixes a {\it keyrec} file for missing keys	 \\
\cmd{cleankrf}		& cleans a {\it keyrec} file of orphaned keys	 \\
\cmd{signset-editor}	& GUI editor for signing sets in a {\it keyrec} file \\
\end{tabular} 
\end{center}
\end{table}

\input{manpages/tools::scripts::zonesigner.tex}
\input{manpages/tools::scripts::genkrf.tex}
\input{manpages/tools::scripts::krfcheck.tex}
\input{manpages/tools::scripts::lskrf.tex}
\input{manpages/tools::scripts::expchk.tex}
\input{manpages/tools::scripts::fixkrf.tex}
\input{manpages/tools::scripts::cleankrf.tex}
\input{manpages/tools::scripts::signset-editor.tex}

\clearpage
\subsection{\bf Zone-Rollover Commands}
\label{ssect-cmds-roll}

The zone-rollover commands provide tools to assist in DNSSEC zone
rollover and keeping records about those zones' rollover status.  The
commands in this group with together with the Zone-Signing Commands
(see Section~\ref{ssect-cmds-sign}.)  These commands are:

\begin{table}[ht]
\begin{center}
\begin{tabular}{ll}
\cmd{rollerd}	& the DNSSEC-Tools key rollover daemon			      \\
\cmd{rollinit}	& create a new {\it rollrec} file			      \\
\cmd{rollchk}	& verify the validity of the contents of a {\it rollrec} file \\
\cmd{lsroll}	& list the contents of a {\it rollrec} file		      \\
\cmd{rollctl}	& communicate with the \cmd{rollerd} rollover daemon	      \\
\cmd{rolllog}	& write a message to the rollover log file		      \\
\cmd{blinkenlights} & GUI tool for monitoring and controlling \cmd{rollerd}   \\
\end{tabular} 
\end{center}
\end{table}

\input{manpages/tools::scripts::rollerd.tex}
\input{manpages/tools::scripts::rollinit.tex}
\input{manpages/tools::scripts::rollchk.tex}
\input{manpages/tools::scripts::lsroll.tex}
\input{manpages/tools::scripts::rollctl.tex}
\input{manpages/tools::scripts::rolllog.tex}
\input{manpages/tools::scripts::blinkenlights.tex}
