
Several libraries have been developed to provide DNSSEC-validated resolution,
translation, and querying services.  These DNSSEC-Tools libraries are:

\begin{description}

\item{\lib{libsres}} - Secure Resolver Library

\lib{libsres} provides the resolver component of the ``validating resolver''.
It is capable of recursively obtaining answers for an application (validator)
from a DNSSEC-aware name server.  Resolver policy will eventually be used to
control the flags (CD, RD etc) that are sent in the query to the name servers,
as well as other parameters, such as the name server to which the query is
to be sent.

This library provides very basic functionality for name resolution.  The data
structures and interfaces exported to applications are still in a state of
flux and are expected to change. Many corner cases are still not supported.

\item{\lib{libval}} - DNSSEC validation library

\lib{libval} provides DNSSEC resource-record validation functionality.  It
relies on the resolver component to fetch answers from a DNSSEC-aware name
server.

As of now there is no functionality to traverse the chain-of-trust while
performing record validation and also no support for validation policies.
As such, the interfaces defined herein are in a state of flux and are
expected to change.

\item{\func{val\_getaddrinfo()}}

Library routines to retrieve DNSSEC-validated network address and service
translations.

\item{\func{val\_gethostbyname()}}

Library routines to perform DNSSEC validation of DNS queries.

\item{\func{val\_query()}}

Library routines to do DNSSEC-validated resolution of DNS queries.

\end{description}

This section contains man pages describing these libraries.

\input{manpages/validator::doc::libsres.tex}
\input{manpages/validator::doc::libval.tex}
\input{manpages/validator::doc::val_getaddrinfo.tex}
\input{manpages/validator::doc::val_gethostbyname.tex}
\input{manpages/validator::doc::val_query.tex}
