\documentclass[12pt]{article}

\pagestyle{headings}
\markboth{DNSSEC-Tools Software User Manual -- Manual Pages}{DNSSEC-Tools Software User Manual -- Manual Pages}

\newenvironment{packed}{\begin{list}{$\bullet$}{\parsep0in\itemsep0in}}{\end{list}}


%
% Macros for specific types of entities.
%
\newcommand{\cmd}[1]{{\bf #1}}
\newcommand{\const}[1]{{\bf #1}}
\newcommand{\func}[1]{{\em #1}}
\newcommand{\lib}[1]{{\em #1}}
\newcommand{\perlmod}[1]{{\bf #1}}
\newcommand{\path}[1]{{\bf #1}}
\newcommand{\struct}[1]{{\em #1}}
\newcommand{\sys}[1]{{\em #1}}
\newcommand{\url}[1]{{\bf #1}}
\newcommand{\var}[1]{{\em #1}}
\newcommand{\xqt}[1]{{\bf #1}}

% \textheight=8.50in
\textheight=9.50in
\voffset=-.10in

\setlength{\textwidth}{6.5in}
\setlength{\oddsidemargin}{0in}

\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{3}

\parindent0em
\parskip0.65em

\hyphenation{DNS-KEY}
\hyphenation{RR-SIG}
\hyphenation{RSA-SHA}
\hyphenation{dns-sec DNS-SEC}
\hyphenation{dns-sec--tools}
\hyphenation{key-rec}
\hyphenation{set-time}
\hyphenation{life-span}
\hyphenation{log-watch}
\hyphenation{tool-options}
\hyphenation{get-host-by-name}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\markboth{DNSSEC-Tools Software User Manual -- Manual Pages}{DNSSEC-Tools Software User Manual -- Manual Pages}

\begin{titlepage}

\vspace{.5in}

\begin{center}
\LARGE{\bf
SOFTWARE USER MANUAL (SUM):
TRAINING, PROCEDURAL, AND
DEVELOPMENT DOCUMENTATION
}
\vspace{1in}

\Large{
DNSSEC-Tools Software User Manual

Manual Pages
\vspace{0.5in}

{\bf Contract: FA8750-04-C-0229
\vspace{0.125in}

CDRL A006}\\
}
27 November 2006
\end{center}

\vspace{.5in}
% \vspace{1.5in}
% \vspace{2.5in}

SUBMITTED BY

SPARTA, Inc.\\
7075 Samuel Morse Dr.\\
Columbia, MD 21046-3401
\vspace{0.25in}

\begin{table}[hb]
\begin{tabular}{lll}
	& Principal Investigator	& Contract/Financial Contact\\
Name	& George R. Mundy		& Kim Morrill\\
Phone	& (410) 872-1515		& (410) 872-1515\\
Fax	& (410) 872-8079		& (410) 872-8079\\
Email	& Russ.Mundy@sparta.com		& Kim.Morrill@sparta.com\\
\end{tabular}
\end{table}

\end{titlepage}
\markboth{DNSSEC-Tools Software User Manual -- Manual Pages}{DNSSEC-Tools Software User Manual -- Manual Pages}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

\begin{center}
{\Large
{\bf DNSSEC-Tools\\
Is your domain secure?}}
\end{center}
\markboth{DNSSEC-Tools Software User Manual -- Manual Pages}{DNSSEC-Tools Software User Manual -- Manual Pages}
\tableofcontents
\markboth{DNSSEC-Tools Software User Manual -- Manual Pages}{DNSSEC-Tools Software User Manual -- Manual Pages}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

\markboth{DNSSEC-Tools Software User Manual -- Manual Pages}{DNSSEC-Tools Software User Manual -- Manual Pages}
\section{About This Document}
\markboth{DNSSEC-Tools Software User Manual -- Manual Pages}{DNSSEC-Tools Software User Manual -- Manual Pages}
\label{sect-about}

The goal of the DNSSEC-Tools project is to create a set of tools, libraries,
patches, applications, wrappers, extensions, and plugins that will help ease
the deployment and maintenance of DNSSEC-related technologies. This document contains manual
pages for the commands, libraries, Perl modules, and data files that are part
of the DNSSEC-Tools distribution.  The document organization is described
below.

\begin{description}

\item
Section~\ref{sect-about} describes the DNSSEC-Tools Software User Manual.

\item
Section~\ref{sect-commands} describes the DNSSEC-Tools commands.  These
commands include programs to analyze and manipulate zone files, maintain the
DNSSEC-Tools environment, and to assist with zone signing and key rollover.
The commands are divided into functional groups:
DNSSEC-Tools maintenance commands (Section~\ref{ssect-cmds-maint}),
DNS zone file commands (Section~\ref{ssect-cmds-zone}),
zone-signing commands (Section~\ref{ssect-cmds-sign}), and
zone-rollover commands (Section~\ref{ssect-cmds-roll}).

\item
Section~\ref{sect-libraries} describes two libraries developed for
DNSSEC-Tools.  The \lib{libsres} library provides secure address resolution
for applications.  The \lib{libval} library provides DNSSEC Resource Record
validation.

\item
Section~\ref{sect-modules} describes a number of Perl modules that were
written to support the DNSSEC-Tools commands.  These modules may be used in
development of additional commands to work with the existing DNSSEC-Tools.

\item
Section~\ref{sect-files} describes data files used by the DNSSEC-Tools
commands, libraries, and modules.

\end{description}

For more information about this project and the tools that are being developed
and provided, please see one of the project web pages at:

\url{http://www.dnssec-tools.org}  \\
\url{http://dnssec-tools.sourceforge.net}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

\subsection{\bf Conventions}

The following typographical conventions are used in this document.

\begin{table}[hb]
\begin{tabular}{lll}
\cmd{command}		& & Command names\\
\const{constant}	& & Code constants\\
\func{call()}		& & System and function calls\\
\lib{library}		& & Library names\\
\perlmod{module}	& & Perl Modules\\
\path{path}		& & File and path names\\
\url{URL}		& & Web URLs\\
\var{variable}		& & Variables\\
\xqt{execution}		& & Simple command executions\\
\end{tabular}
\end{table}

Longer sets of command sequences are given in this format:
\begin{verbatim}
        # cd /tmp
        # ls
        # rm -fr *
\end{verbatim}
In most cases, output will not be displayed for given command sequences.

\vspace{.25in}

\subsection{\bf Comments}

Please send any comments and corrections to developers@dnssec-tools.org.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

\markboth{DNSSEC-Tools Software User Manual -- Manual Pages}{DNSSEC-Tools Software User Manual -- Manual Pages}
\section{DNSSEC-Tools Commands}
\markboth{DNSSEC-Tools Software User Manual -- Manual Pages}{DNSSEC-Tools Software User Manual -- Manual Pages}
\label{sect-commands}

\input{man-cmds}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

\markboth{DNSSEC-Tools Software User Manual -- Manual Pages}{DNSSEC-Tools Software User Manual -- Manual Pages}
\section{DNSSEC Library Routines}
\markboth{DNSSEC-Tools Software User Manual -- Manual Pages}{DNSSEC-Tools Software User Manual -- Manual Pages}
\label{sect-libraries}

\input{man-libs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

\markboth{DNSSEC-Tools Software User Manual -- Manual Pages}{DNSSEC-Tools Software User Manual -- Manual Pages}
\section{Supporting Modules}
\markboth{DNSSEC-Tools Software User Manual -- Manual Pages}{DNSSEC-Tools Software User Manual -- Manual Pages}
\label{sect-modules}

\input{man-modules}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

\markboth{DNSSEC-Tools Software User Manual -- Manual Pages}{DNSSEC-Tools Software User Manual -- Manual Pages}
\section{Data Files}
\markboth{DNSSEC-Tools Software User Manual -- Manual Pages}{DNSSEC-Tools Software User Manual -- Manual Pages}
\label{sect-files}

\input{man-files}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
