
\clearpage
\subsection{Creating a Signed Delegation in a Child Zone}
\label{delegation-child}

This section describes the steps required to create a signed delegation in a
child zone.

See Figure~\ref{fig:securingdeleg-child}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Check the Keyset File}

Ensure that the keyset file (generated in~\ref{signzone-no-deleg}
or~\ref{signzone-has-deleg}) contains the correct KSK.  A visual comparison
of the key material in the keyset file with the actual key contents will
determine this.  Also, ensure that the key-tags in the keyset file correspond
to the tags that were recorded for the KSK in in~\ref{signzone-nodel}
or~\ref{signzone-hasdel}.

\begin{tabbing}
\hspace{0.5in} 12345678 \= 12345678 \= 12345678 \= 12345678 \= 12345678 \= 12345678 \= 12345678 \kill \\
\hspace{0.5in}\$ {\bf cat keyset-\underline{zonefile}} $[$ENTER$]$ \\
\hspace{0.5in} \underline{zone.name} \> \> \> 3600 IN \> DNSKEY 257 3 5 ( \\
\hspace{0.5in} \> \> \> \> \> ... \\
\hspace{0.5in} \> \> \> \> ); key id = key-tag \\
\hspace{0.5in}\$ \\
\end{tabbing}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Securely Transfer the Keyset to the Parent}

If any of the zone's KSKs have changed since the last time this file was sent
to the parent, then the keyset must also be transferred to the parent.
If none of the zone's KSKs have changed, this step may be skipped.

This is not required during a ZSK roll-over.  See Sections \ref{roll-curzsk},
\ref{roll-emergency-curzsk}, \ref{roll-emergency-pubzsk}, and
\ref{roll-emergency-zsks}.

Secure communication between the parent and child zone is done out-of-band.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Wait for the Parent to Publish the DS Record}

Before proceeding, wait for the parent zone to publish the DS record.  This
may be found by using the \cmd{dig} command to retrieve the zone's DS record.
The \option{aa} flag in the result must be set and the ANSWER section must
not be empty.

You may continue if the DS record is the same as the value in the file
generated in~\ref{signzone-no-deleg} or~\ref{signzone-has-deleg}.

\begin{tabbing}
\hspace{0.5in}\$ {\bf dig @\underline{parent-IP-address} DS \underline{zone.name}} $[$ENTER$]$ \\
\hspace{0.5in} ; $<$$<$$>$$>$ DiG 9.3.0 $<$$<$$>$$>$ ... \\
\hspace{0.5in} ... \\
\hspace{0.5in} ;; flags: qr aa rd; QUERY: 1, ANSWER: 1, AUTHORITY: 1, ADDITIONAL: 0 \\
\hspace{0.5in} ... \\
\hspace{0.5in} ;;ANSWER SECTION \\
\hspace{0.5in} 12345678 \= 12345678 \= 12345678 \= 12345678 \= 12345678 \= 12345678 \kill \\
\hspace{0.5in} \underline{zone.name} \> \> 3600 \> IN \> DS \> ... \\
\hspace{0.5in} ... \\
\hspace{0.5in}\$ \\
\end{tabbing}

