
\clearpage
\subsection{Current ZSK Roll-Over}
\label{roll-curzsk}

This section gives the steps necessary for the pre-publish scheme for ZSK
roll-over.  The alternative, the double-signature method, is used for rolling
over KSKs.  Double signatures for records signed by the ZSK can increase the
size of the zone many times.  The pre-publish scheme, although requiring more
steps for the roll-over, does not suffer from this problem. The size argument
does not apply during KSK roll-over since the DNSKEY RRset is the only record
doubly signed by the KSK.

See Figure~\ref{fig:zskroll}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Ensure that Sufficient Time has Elapsed Since the Last Roll-Over}

The time between roll-overs has to be at least twice the maximum zone TTL
period.  This is the largest TTL in the entire zone file multiplied by two.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Sign Zone with the KSK and Published ZSK}

Follow steps \ref{check-zonefile-unsigned-nodeleg}~--~\ref{signzone-nodel-last}
if the zone does no delegation.  Follow steps
\ref{check-zonefile-unsigned-deleg}~--~\ref{signzone-deleg-last} if the
zone does delegation.  The ZSK used in the signing process in
Section~\ref{signzone-no-deleg} or~\ref{signzone-has-deleg} must be the key
that is marked as the Published key (P) in the key-tag table. The KSK used
as input to \cmd{dnssec-signzone} does not change, so the keyset does not
change and does not have to be re-sent to the parent.

Record the signature expiry date in the key-tag table.

\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\hline
{\bf Zone} &
\multicolumn{4}{c|}{{\bf ZSK}} &
\multicolumn{4}{c|}{{\bf KSK}} &
{\bf Exp} \\
\cline{2-9}

 & Tag & Size & Creat & S & Tag & Size & Creat & S & \\
\hline

\underline{zone.name}	&
\underline{zsktag-cur}	&
512			&
\underline{date}	&
C			&
\underline{ksktag}	&
1024			&
\underline{date}	&
C			&
\underline{date}	\\

\cline{2-9}

			&
\underline{zsktag-pub}	&
512			&
\underline{date}	&
P			&
& & & & \\

\hline
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{zone-reload}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Wait for Old Zone Data to Expire from Caches}

Wait at least twice the maximum zone TTL period for the old zone data to
expire from name server caches.  This is the largest TTL in the entire zone
file multiplied by two.  This will also allow the new data to propagate.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{keygen-zsk-keytag}
\input{update-zonefile-newzsk}
\input{keytag-delcurzsk}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Sign the Zone with the KSK and Current ZSK}

\input{signzone-curzsk-msg}

Record the signature expiry date in the key-tag table.

\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\hline
{\bf Zone} &
\multicolumn{4}{c|}{{\bf ZSK}} &
\multicolumn{4}{c|}{{\bf KSK}} &
{\bf Exp} \\
\cline{2-9}

 & Tag & Size & Creat & S & Tag & Size & Creat & S & \\
\hline

\underline{zone.name}	&
\underline{zsktag-pub}	&
512			&
\underline{date}	&
C			&
\underline{ksktag}	&
1024			&
\underline{date}	&
C			&
\underline{date}	\\

\cline{2-9}

			&
\underline{zsktag-new}	&
512			&
\underline{date}	&
P			&
& & & & \\

\hline
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{zone-reload}
\input{delete-old-zsk}
